Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-04 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

The Kochen-Specker theorem can be proved easily by considering a pair
of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\[
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}
\]

>>>>

The Kochen-Specker theorem can be proved easily by considering a pair
of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
In the original proof, we assign value to each observable, where operators
in each row and column commutes, and each operator is the product
of the two others, except in the third column. Because of 
\begin{equation}
\left(\sigma_{x}\otimes\sigma_{z}\right)\left(\sigma_{z}\otimes\sigma_{x}\right)=\sigma_{y}\otimes\sigma_{y}=-\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)\textrm{ ,}
\end{equation}
it is clear impossible to attribute to each operator in equation~(\ref{eq:MerminSquare})
numerical values, $1$ or $-1$, which obey the same multiplication
rule as the operators themselves.

\begin{table}
\caption{\label{table:commonBasis}Observables and their common eigenbasis.
In order to unified and simplify notation, we do , and not normalize
eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Operators} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
When we reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column as in table~\ref{table:commonBasis}.
